### 2013-09-10 mcmc.tex
integrals and histograms

@@

...Why is it that the sampling is only really useful for computing integrals.  More on this below...

...Is there any way to reconstruct $p(x)$ from the samples
$\setof{x_k}$?  In short, no, but in many cases of interest, sort-of!..

>>>>

The ``correctness'' of a sampling is defined (above) in terms of its use in
  performing integrals or approximate computation of integrals.
In a deep sense, the \emph{only} thing a sampling is good for is
  computing integrals.
There are many uses of the MCMC sampling, some of them good and some of them bad.
Most of the good or sensible uses will somehow involve integration.

For example, one magical property of a sampling (in a $d$-dimensional space)
  is that a \emph{histogram} (a $d$-dimensional histogram) of the samples
  (divided, if you like, by the number of samples in each bin and the bin width\note{something about units and normalization})
  looks very much like the pdf from which the samples were drawn.
This is a way to ``reconstruct'' the pdf from the sampling:
Make a histogram from the samples.
Even in this case, the sampling is being used to do \emph{integrals};
  the (possibly odd) idea is that the approximate or effective value of the pdf in each bin
  of the histogram is an average over the bin.
That average is obtained by performing an integral.

@@
